Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-30 article.qmd
Clarify download from BioModels
Implemented reactions

For reaction networks,
we are interested in first-order differential equations
relating the rate of change of the species.
To facilitate defining these models,
SimBio defines `Species`,
which comprises of a `poincare.Variable` and an stoichiometry,
and `Reaction`,
which transform reactants into products taking into account the stoichiometry (@fig-simbio).
It also includes `MassAction`, a `Reaction` subclass,
which automatically adds the reactants as part of the rate law (@fig-simbio).
Several commonly used reactions are predefined as `MassAction` subclasses.
Additionally, SimBio supports importing from and exporting to SBML,
or directly from BioModels (@fig-simbio-io).

>>>>

For reaction networks,
we are interested in first-order differential equations
relating the rate of change of the species.
To facilitate defining these models,
SimBio defines `Species`,
which comprises of a `poincare.Variable` and an stoichiometry,
and `Reaction`,
which transform reactants into products taking into account the stoichiometry (@fig-simbio).
It also includes `MassAction`, a `Reaction` subclass,
which automatically adds the reactants as part of the rate law (@fig-simbio).
Several commonly used reactions are predefined as `MassAction` subclasses,
such as
`MichaelisMenten` ($S + E \rightarrow ES -> P + E$)
and its approximate form without the intermediate species $ES$,
and it is also simple to implement your own as subclasses of `Reaction` or `MassAction`.
Additionally, SimBio supports importing from and exporting to SBML,
and downloading them directly from BioModels (@fig-simbio-io).
